---
title: "Practice Versioning (Forked Version)"
author: "ADD YOUR NAME"
date: "2026-01-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Complete the following five code chunks to complete a mini-analysis.  

Stage, commit, and push versions of the analysis after:
1. Completing it for the first time such that it knits successfuly (set eval = T first), add name to YAML
2. Changing the plot variable (y mapping) and associated text narrative
3. Creating a bug in the code that causes a problem during knitting (but before you fix it)
4. Fixing the bug and confirming the fix with a commit message
5. Polishing the code by adding unique chunk labels and improving use of headers, bold, italics, etc. and polish the figure


Step 1. Load Libraries

Load the tidyverse and palmerpenguins datasets

```{r eval = F}
library(tidyverse)
library(___)
```

Step 2. Glimpse the dataset object `penguins`

```{r eval = F}
___(penguins)
```

Step 3. Plot the variable `flipper_length_mm` against species using a box plot

```{r eval = F}
___ %>%
  ggplot(aes(
    x = ___,
    y = ___,
  )) +
  geom_boxplot() +
  theme_classic()
```

Step 4. Create a new variable called `flipper_length_cm`

```{r eval = F}
___ %>%
  mutate(___ = flipper_length_mm / 10)
```

Step 5. Assign the table including the new variable to an object called `penguins_cm`

```{r eval = F}
penguins_cm ___ ___ %>%
  mutate(___ = flipper_length_mm / 10)
```




